---
title: "Eurovision"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(here)
library(readr)
library(dplyr)
library(ggplot2)
library(here)
library(tidyr)
library(purrr)
library(DT)
library(shiny)
```


# About 

Eurovision is a popular music computation that includes many teams from all over 
Europe each representing their nation. It's been on for several decades. The dataset
consists info on all teams that have participated since 1951 and their rankings.
More information about them can be found here. 
https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-05-17/readme.md



# Data 

This is what the data looks like. The raw file can be downloaded from 
https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-05-17/eurovision.csv

```{R}


if(!file.exists(here("data"))){
  dir.create(here("data"))
}
url<- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-17/eurovision.csv"
if(!file.exists(here("data", "eurovision.csv"))){
  download.file(url, here("data", "eurovision.csv"))
}


```

```{R }
euro <- read_csv(here("data", "eurovision.csv"))

euro |> head(100) |> DT::datatable()

```

# Static 1

Row {data-height=650}
-------------------------------------

### First chart 

```{R, echo = FALSE}

euro_sections <- euro |> select(artist_country, section)
euro_sections <- euro_sections |> group_by(artist_country, section) |> summarise(n = n())
euro_sections_2 <- euro_sections |> group_by(section)

g <- ggplot(euro_sections, aes(x = artist_country, y = n )) + geom_bar(stat = "identity")+ 
  facet_wrap(~section)+
  scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5, size = 6)) + theme(axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5, size = 3.4)) +coord_flip() + labs(title= " number of times countries appeared in high-ranking sections", subtitle= "5 sections", caption = "sourced from tidytuesday")
g

```

# Static 2

Column {.tabset}
-------------------------------------
   
### Chart 2

```{r}

euro$rank_lgl <- euro$rank |> map_lgl(function(x) x<=5)

euro_true <- euro |> group_by(rank_lgl, artist_country) |> summarise(n = n()) |> filter(rank_lgl == TRUE)
euro_false <- euro |> group_by(rank_lgl, artist_country) |> summarise(n = n()) |> filter(rank_lgl == FALSE)


euro_true_and_false <- inner_join(euro_true, euro_false, by = "artist_country")
euro_true_and_false <- euro_true_and_false |> mutate(prop = n.x/(n.x + n.y) )



g_2 <- ggplot(euro_true_and_false, aes(x = artist_country, y = prop)) + geom_point() +scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6)) + labs(title= "Proportion of instances where country was Top 5", subtitle= " 47 countries", caption = "sourced from tidytuesday")
g_2

```   
 
### Chart 3
    
```{r}
euro_won <- euro |> group_by(winner, artist_country) |> summarise(n = n()) |> filter(winner == TRUE)
g_3 <- ggplot(euro_won, aes(x = n)) + geom_dotplot(binwidth = 0.5) +scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6)) + labs(title= "Frequency of number of times countries won", subtitle= "49 countries", caption = "sourced from tidytuesday")
g_3
```

# Int 1 

Column {.sidebar}
-------------------------------------

Histogram counting number of times each country appeared in the top 5 ranks 

```{R }

selectInput("ranks", label = "Toggle between top 5 ranks",
            choices = c(1, 2,3,4,5), selected = 1 )

```


Column 
-------------------------------------
```{R}

renderPlot({
  
  ranks <- euro |> filter(rank == input$ranks ) |> count(artist_country) 
  title1 <- paste0("Frequency of number of times countries came rank ", as.character(input$ranks))
  sub1 <- paste0( as.character(nrow(ranks)),  " countries")
    
  ggplot(ranks, aes(x = artist_country, y = n)) + geom_bar(stat = "identity") + scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10)) + labs(title= title1, subtitle= sub1, caption = "sourced from tidytuesday")
})

```

# Int 2


# Analysis 

For an example analysis using `tidylog` I'll be using the `eurovision` dataset found in `tidytuesday`. The dataset and dictionary can be found [here.](https://github.com/rfordatascience/tidytuesday/tree/master/data/2022/2022-05-17)

LOAD LIBRARIES

```{R}

library(here)
library(readr)
library(dplyr)
library(ggplot2)
library(here)
library(tidyr)
library(purrr)
library("tidylog")
```

SAVE DATA

```{R}


if(!file.exists(here("data"))){
  dir.create(here("data"))
}
url<- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-17/eurovision.csv"
if(!file.exists(here("data", "eurovision.csv"))){
  download.file(url, here("data", "eurovision.csv"))
}


```

LOAD DATA

Goal of the analysis is to define the success of countries.

We'll be looking at the number of times countries came up as finalists.

The number of times a country was top 5.

The number of times the country won.

```{R}

euro <- as_tibble(read_csv(here("data","eurovision.csv")))

```

The number of times a country showed up in high-ranking sections

i.e., finals, semifinals etc.

We'll be looking at the `artist_country` and `section` variables.

```{R, echo=TRUE }
distinct(euro, across(artist_country))
distinct(euro, across(section))
```

Turns out there are 52 distinct countries and 5 distinct sections.

```{R, echo=TRUE }

euro_sections <- euro |> select(artist_country, section)
euro_sections <- euro_sections |> group_by(artist_country, section) |> summarise(n = n())
euro_sections_2 <- euro_sections |> group_by(section)


```

```{R, echo = TRUE }

euro_sections <- euro |> select(artist_country, section)
euro_sections <- euro_sections |> group_by(artist_country, section) |> summarise(n = n())
euro_sections_2 <- euro_sections |> group_by(section)


```

```{R, echo = TRUE }
split_euro <- group_split(euro_sections_2)

final_countries <- split_euro |> purrr::map(function(x) x[which.max(x$n), ])

# 
# 
# [[1]]
# # A tibble: 1 × 3
#   artist_country section     n
#   <chr>          <chr>   <int>
# 1 Germany        final      48
# 
# [[2]]
# # A tibble: 1 × 3
#   artist_country section              n
#   <chr>          <chr>            <int>
# 1 Belgium        first-semi-final    12
# 
# [[3]]
# # A tibble: 1 × 3
#   artist_country section         n
#   <chr>          <chr>       <int>
# 1 France         grand-final    19
# 
# [[4]]
# # A tibble: 1 × 3
#   artist_country section               n
#   <chr>          <chr>             <int>
# 1 Denmark        second-semi-final    10
# 
# [[5]]
# # A tibble: 1 × 3
#   artist_country section        n
#   <chr>          <chr>      <int>
# 1 Andorra        semi-final     4


```

Turns out that Germany has been in the finals 48 times so far and France has been in the grand-final 19 times!


### Plot Histogram

```{R, echo =FALSE}
g <- ggplot(euro_sections, aes(x = artist_country, y = n )) + geom_bar(stat = "identity")+ 
  facet_wrap(~section)+
  scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5, size = 6)) + theme(axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5, size = 3.4)) +coord_flip() + labs(title= " number of times countries appeared in high-ranking sections", subtitle= "5 sections", caption = "sourced from tidytuesday")
g

```

### Cleaning 

```{R, echo = TRUE}

euro$rank_lgl <- euro$rank |> map_lgl(function(x) x<=5)

euro_true <- euro |> group_by(rank_lgl, artist_country) |> summarise(n = n()) |> filter(rank_lgl == TRUE)
euro_false <- euro |> group_by(rank_lgl, artist_country) |> summarise(n = n()) |> filter(rank_lgl == FALSE)


euro_true_and_false <- inner_join(euro_true, euro_false, by = "artist_country")
euro_true_and_false <- euro_true_and_false |> mutate(prop = n.x/(n.x + n.y) )


### TIDYLOG OUTPUT ###
# group_by: 2 grouping variables (rank_lgl, artist_country)
# summarise: now 140 rows and 3 columns, one group variable remaining (rank_lgl)
# filter (grouped): removed 93 rows (66%), 47 rows remaining
# group_by: 2 grouping variables (rank_lgl, artist_country)
# summarise: now 140 rows and 3 columns, one group variable remaining (rank_lgl)
# filter (grouped): removed 88 rows (63%), 52 rows remaining
# inner_join: added 4 columns (rank_lgl.x, n.x, rank_lgl.y, n.y)
#             > rows only in x  ( 0)
#             > rows only in y  ( 5)
#             > matched rows     47
#             >                 ====
#             > rows total       47
# mutate: new variable 'prop' (double) with 41 unique values and 0% NA
 
```

Let's look at proportion of instances where country was top 5.


### Proportion
```{R proportion, echo = FALSE}

g_2 <- ggplot(euro_true_and_false, aes(x = artist_country, y = prop)) + geom_point() +scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6)) + labs(title= "Proportion of instances where country was Top 5", subtitle= " 47 countries", caption = "sourced from tidytuesday")
g_2
```


### Plot Histogram
```{R , echo = FALSE}
euro_won <- euro |> group_by(winner, artist_country) |> summarise(n = n()) |> filter(winner == TRUE)
g_3 <- ggplot(euro_won, aes(x = n)) + geom_dotplot(binwidth = 0.5) +scale_x_discrete(label=abbreviate) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6)) + labs(title= "Frequency of number of times countries won", subtitle= "49 countries", caption = "sourced from tidytuesday")
g_3
```

### Functions used

1.  dplyr:: distinct, across, select , group_by, summarise, n, group_split, inner_join, mutate

2.  purrr:: map, map_lgl

3.  ggplot:: geom_bar, geom_point, geom_dotplot

