---
title: "Eurovision"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```


# About 

Eurovision is a popular music computation that includes many teams from all over 
Europe each representing their nation. It's been on for several decades. The dataset
consists info on all teams that have participated since 1951 and their rankings.
More information about them can be found here. 
https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-05-17/readme.md



# Data 
stuff https://rsconnect.biostat.jhsph.edu/ocs-bp-school-shootings-dashboard/#section-the-data

# Static 1

# Static 2

# Int 1 

#Int 2

# Chart 1 

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

